Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-16 awipev-CO2.Rmd

d_all <- d_all%>%
  dplyr::mutate( sal = ifelse(sal <28, NA, sal) ,
                 sal_fb = ifelse(sal_fb <28, NA, sal_fb),
                 sal_insitu = ifelse(sal_insitu <28, NA, sal_insitu))

>>>>

d_all <- d_all%>%
  dplyr::mutate( sal = ifelse(sal <28, NA, sal) ,
                 sal_fb = ifelse(sal_fb <28, NA, sal_fb),
                 sal_insitu = ifelse(sal_insitu <28, NA, sal_insitu))
  d_all <- d_all%>%
  dplyr::mutate( sal = ifelse(datetime > "2019-12-26 00:00:00", NA, sal),
                 sal_insitu = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu))
